---
title: "HW2_linearReg"
author: "Jie Hu"
date: "April 19, 2016"
output: html_document
---

#### 2.1

a. the conclusion is not warranted, because CL involves slope equals to 0 which means X and Y has no relationship. The implied significance level is 0.95
b. intercept can be negative. The valid range of X might not allow Y to be negative but the regression line can have negative intercept.

#### 2.2
No, we can only say there’s no convincing evidence that there’s relationship between X and Y.

#### 2.6
```{r}
X <- c(1,0,2,0,3,1,0,1,2,0)
Y <- c(16,9,17,12,22,13,8,15,19,11)

df <- data.frame(X,Y)
model_6 <- lm(Y~X, data = df)

# Confidence Interval for slope and intercept
confint(model_6, level = 0.99)


# Plot model and confidence interval
newdata <- data.frame(X = seq(1, 3, 0.05))
predict(lm(Y ~ X), interval = "confidence")

pred.w.plim <- predict(lm(Y ~ X), newdata, interval = "prediction")
pred.w.clim <- predict(lm(Y ~ X), newdata, interval = "confidence")
matplot(newdata$X, cbind(pred.w.clim, pred.w.plim[,-1]),
        lty = c(1,2,2,3,3), type = "l", ylab = "predicted y")
```

b.
```{r}
# Estimators
summary(model_6)
```

$$H_0: \beta_1 = 0$$
$$H_A: \beta_1 \ne 0$$

test for code `summary(cars)`


